\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the input with the weight vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

As can be seen, the operations iterate over the matrix p five times - once to add the bias, three times to calculate the softmax, and once to search for the best class. We shall use a popular method, kernel fusion~\citep{Guevara2009EnablingTP}, to optimize the output layer.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Find-1-Best}{vector $p$, bias vector $b$}

@@

\end{algorithmic}
\caption{Find 1 best only}
\label{algo:Argmax only}
\end{algorithm}

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
%\REQUIRE source sentence $s$, translation options
\While{more input} 
  \State Create batch $b$
  \State Encode($b$)
  \While{batch is not empty} 
    \State Decode($b$)
    \ForAll{sentence $s$ in $b$}
      \If{translation is complete}
        \State Remove $s$ from $b$
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

>>>>

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the weight matrix with the input vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

As can be seen, the operations iterate over the matrix p five times - once to add the bias, three times to calculate the softmax, and once to search for the best class. We fuse the three operation into one kernel, a popular optimization technique~\citep{Guevara2009EnablingTP}.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused-kernel-1-best}{vector $p$, bias vector $b$}

@@

\end{algorithmic}
\caption{Find 1-best only}
\label{algo:Argmax only}
\end{algorithm}

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
\While{more input} 
  \State Create batch $b$
  \State Encode($b$)
  \While{batch is not empty} 
    \State Decode($b$)
    \ForAll{sentence $s$ in $b$}
      \If{translation is complete}
        \State Remove $s$ from $b$
      \EndIf
    \EndFor
  \EndWhile
\EndWhile
